Draft information

### 2019-06-17 paper/draft-info.Rmd
Update draft info

* Specify grant numbers in the Acknowledgements and make sure the ones stated there now are correct. 
* Suggestions to bring the abstract down to 150 words.
* Approve (or not) for submission.

>>>>

* Should I include more data?

## Done

* Downloaded network data from the Web of Life and cleaned it. I didn't anticipated data needed SO MUCH work! I estimated three days to do this but took roughly 3 weeks to do it propperly and there is still some work to do. Quite a mess...

## To-do

* Manually fix the remaining species names that are incorrect and were not picked up by the automatic procedure
* Fix references. There are lots of mistakes re. author, years and publication venue.
